### 2020-02-20 Article.tex
colorings

We define tree $T$ as a connected hypergraph such that
$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
as a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its root. We will
usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. We define the set
of initial edges of a vertex-rooted tree $(T,v)$ as the
set of edges in $T$ that contain $v$. \par
%
%Similarly, we define an edge-rooted tree $(T,e,v)$
%as a tree $T$ with a distinguished edge $e\in E(T)$ and
%a distinguished vertex $v\in e$. \par
Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
we define $Tree_{(T,v)}(u)$ as the tree $T[X]$ induced on the
set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
$, to which we assign $u$ as the root.
That is, $Tree_{(T,v)}(u)$ is the tree consisting of those vertices
whose only path to $v$ contains $u$.
\par
We define the radius of a vertex-rooted, or edge-rooted,
tree as the maximum distance between its marked
vertex and any other one. \par

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

@@

\begin{theorem}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{definition}
	We call an hypergraph $G$ \textbf{saturated} if any proper 
	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
	The \textbf{center} of a connected hypergraph $G$ is the maximal saturated
	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
	the center of an hypergraph is the union of the
	centers of its connected components. 
\end{definition}

@@

\begin{definition}
	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
	and let $v\in V(G)$.
	Consider the graph $G^\prime= G\setminus 
	E\big(Center(G,\overline{u})\big)$. Then the connected components of
	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
	$G(\overline{u})$}, denoted by $Tree(G\big(\overline{u}),v\big)$,
	to the connected component of $G^\prime$ to which $v$ belongs
	with $v$ as its root. \par   
\end{definition}

Let $\overbar{v}\in \N*$ a list of vertices. For each $n,r\in \N$ and 
$v_i\in \overbar{v}$ we define the random hypergraph
$T_n(v_i,\overbar{v};r)$ in the following way: Let $G^\prime_n:=G_n \setminus
E(G_n[\overbar{v}])$. Then $T_n(v_i,\overbar{v};r):= N^{G^\prime_n}(v;r)$.
That is, $T_n(v_i,\overbar{v};r)$ is the $r$-neighborhood of $v_i$ in ``$G_n$
minus the edges induced on $\overbar{v}$".

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
		list of different vertices that are contained in $\overbar{w}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	
		\item[(3)] 	
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex, then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)=1. \]	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.  \par

	\end{proof}

Let $\overbar{\mathcal{T}}$ be a  $\overbar{u}\in N$

@@

%scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
%$\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 

@@

%$\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par

@@

%$0\leq p \leq 1$ in the real numbers, is the discrete probability space over

@@

%$n$ tends to infinity. \par

@@

%$\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends

@@

%$\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 

@@

%$\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 

@@

%$\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO

@@

%$\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being

@@

%$\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par

@@

%$p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 

@@

%$\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
%$p=\beta n^{k-1}$.

@@

%The first order language with signature $\sigma$ deals with strings
%of symbols taken from the alphabet consisting of
% variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
%the logical connectives $\neg, \wedge, \vee$,
%the universal $\forall$ and existential $\exists$ quantifiers,
%the equality symbol, and the parentheses $),($.
%A first order formula is a string obtained after applying the
%following set of rules a finite number of times: 
%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
%	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
%	and $t_1,\dots, t_{a_i}$ are terms then 
%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
%	\item If $\varphi$ and $\psi$ are formulas, then both
%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
%	a formula.
%	\item If $\varphi$ is a formula and $x$ is a variable then both
%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
%\end{enumerate} 
%
%Let $\varphi$ be a first order formula. An occurrence of a variable 
%in $\varphi$ is called bounded if it is within the scope of
%a quantifier binding it, and is called free otherwise. We
%will assume that the occurrences of any given variable in a first
%order sentence are either all free or all bounded. 
%We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
%that $x_1, \dots, x_n$ are distinct and they are the free variables
%(i.e. the variables whose occurrences are all free) 
%in $\varphi$. A formula with no free variables is called a sentence,
%and a formula whose variables are all free is called open.
%
%Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
%be a first order sentence. Given a map $\alpha$ from the set
%of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
%of $\mathfrak{A}$ we define the relation 
%$\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
%in the following way:
%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
%	\item 
%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
%	and $t_1,\dots, t_{a_i}$ are terms then 
%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
%	\item If $\varphi$ and $\psi$ are formulas, then both
%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
%	a formula.
%	\item If $\varphi$ is a formula and $x$ is a variable then both
%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
%\end{enumerate} 
%
%

@@

%$[n]:= \{1,\dots, n\}$. We will denote by $S_n$

@@

%$(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
%$[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the

@@

%$1,\dots, c$, sizes $a_1,\dots,a_c$, 

@@

%$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
%$[n]$. Also, we will write $H(G)$ to denote the 

>>>>

We define tree $T$ as a connected hypergraph such that
$ex(T)=-1$. We define a vertex-rooted tree $(T,v)$ 
as a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its root. We will
usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. We define the set
of initial edges of a vertex-rooted tree $(T,v)$ as the
set of edges in $T$ that contain $v$. \par
%
%Similarly, we define an edge-rooted tree $(T,e,v)$
%as a tree $T$ with a distinguished edge $e\in E(T)$ and
%a distinguished vertex $v\in e$. \par
Given a rooted tree $(T, v)$, and a vertex $u\in V(T)$, 
we define $\tau_{(T,v)}(u)$ as the tree $T[X]$ induced on the
set $X:=\{ \, w\in V(T) \, | \, d(v,w)=d(v,u)+ d(u,w) \,  \}
$, to which we assign $u$ as the root.
That is, $\tau_{(T,v)}(u)$ is the tree consisting of those vertices
whose only path to $v$ contains $u$.
\par
We define the radius of a vertex-rooted, or edge-rooted,
tree as the maximum distance between its marked
vertex and any other one. \par

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[\tau_{(T_1,v_1)}(u)\morph{k} \tau_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

@@

\begin{theorem} \label{thm:BrunSieve}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{definition}
	We call an hypergraph $G$ \textbf{saturated} if any proper 
	sub-hypergraph $G^\prime \subset H$ satisfies $ex(G^\prime)<ex(G)$. \par
	The \textbf{center} of a connected hypergraph $G$ is its maximal saturated
	sub-hypergraph and it is denoted by $Center(G)$. In the general case 
	the center of an hypergraph is the union of the
	centers of its connected components. 
\end{definition}

@@

\begin{definition}
	Let $G$ be an hypergraph $G$, let $\overline{u}\in V(G)^*$
	and let $v\in \overline{u}$.
	Consider the graph $G^\prime= G\setminus 
	E\big(Center(G,\overline{u})\big)$. Then the connected components of
	$G^\prime$ are all trees. We call the \textbf{tree of $v$ in
	$G(\overline{u})$}, denoted by $Tr\big(G(\overline{u}),v\big)$,
	to the connected component of $G^\prime$ to which $v$ belongs
	with $v$ as its root. \par   
	In this same situation, let $r\in \N$ and $H:=N^G(\overline{u};r)$.
	We call the \textbf{$r$-tree of $v$ in $G(\overline{u})$}, 
	denoted by $Tr\big(G(\overline{u}),v;r\big)$ to 
	$Tr\big(H(\overline{u}),v\big)$.
\end{definition}

\newpage

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$ 
	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	 \par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
\end{definition}

\begin{theorem} 
	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
	rooted $\Sigma_i$-trees. 
	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
	the limit
	\[
	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
	\]
	exists and does not depend on the chosen $w$. For each 
	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
	Given a tree $T\in \mathcal{T}_i$ let
	\[
	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
	\]	
\end{theorem}

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overline{u}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be a consistent
		open sentence (i.e. with no bounded variables) such that 
		$length(\overbar{x})=length(\overbar{w})$.
		Let $=v_1,\dots,v_k \in \N$ be different vertices
		contained in $\overline{u}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by the correspondent
		$r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	 	
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{u}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		Tr\big(G_n(\overbar{u}),v_i;r\big)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]=1. \]	 	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.  \par
		Let $T_{n,i}=Tr\big(G_n(\overbar{u}),v_i;r\big)$. 
		Let $i\in [k]$ and let $\mathcal{E}$ be any $k$-equivalence class
		of initial edges of radius at most $r_i$. Then we define $X_{n,i,\mathcal{E}}$
		as the random variable that counts the number of initial edges $e$ such that
		$(T_{n,i},e)\in \mathcal{E}$.\par
		We are going to show that the variables $X_{n,i,\mathcal{E}}$ converge, as
		$n$ tends to infinity, to independent Poisson variables 
		$\mathrm{Poiss}(\mu_{r_i,\mathcal{E}})$ whose means $\mu_{r_i,\mathcal{E}}$ 
		are expressions in the family $M$. That is,
		\begin{equation} \label{eqn:PoissonEdges}
		\Ln \mathrm{Pr}\big(
		\bigwedge_{i=1}^k \bigwedge_{\mathcal{E} \in EDGE_{r_i}} X_{n,i,\mathcal{E}}=a_{i,\mathcal{E}}
		\, | \, \sigma(\overline{w})\big) =
		\prod_{i=1}^k \prod_{\mathcal{E} \in EDGE_{r_i}} e^{-\mu_{r_i,\mathcal{E}}}
		\frac{\mu_{r_i,\mathcal{E}}^{a_{i,\mathcal{E}}}}{a_{i,\mathcal{E}}!}
		\end{equation}
		Furthermore, for each $i$ and $\mathcal{E}$ we will prove that the mean 
		$\mu_{r_i,\mathcal{E}}$ does only depend on $r_i$ and $\mathcal{E}$.
		This proves both (1), and (2).\par

		We will prove \cref{eqn:PoissonEdges} using \cref{thm:BrunSieve}.
		For each $i\in [k]$ and $\mathcal{E}\in EDGE_{r_i}$ we define $\mu[r_i,\mathcal{E}]$
		in the following way. Let $(T,e)$ be a representative of the equivalence class
		$\mathcal{E}$. Let $p$ be the root of $T$ and let $j$ be the color of $e$. 
		Let $b$ be the number of bijections $f:e\rightarrow e$ satisfying that (1)
		$f(p)=p$, and (2) for any $q\in e$ different from $p$
		$\tau_{(T)}(q) \simeq_k \tau_{(T)}(f(q))$. For any $q\in e$ 
		different from $p$, let $\mathcal{T}_q$ be the $k$-equivalence class
		of the tree $\tau_{(T)}(q)$. Then
		\[
		\mu_[r_i,\mathcal{E}]=\frac{\beta_j}{b} \prod_{\substack{q\in e \\ q\neq p}} 
		\mathrm{Pr}[r_i-a_j+1,\mathcal{T}_q].
		\]

		Now we have to prove that for any non-negative numbers, 
		$(d_{i,\mathcal{E}})_{\substack{i\in [k]}\\
		\mathcal{E}\in EDGE_{r_i}}$, it is satisfied
		\[\Ln
		\mathrm{E}\left[
		\prod_{\substack{\substack{i\in [k]}\\
				\mathcal{E}\in EDGE_{r_i}}} \binom{X_n[i,\mathcal{E}]}{d[i,\mathcal{E}]}
		\right] = \prod_{\substack{\substack{i\in [k]}\\
				\mathcal{E}\in EDGE_{r_i}}} \frac{\mu[r_i,\mathcal{E}]^{d[i,\mathcal{E}]}}
			{d[i,\mathcal{E}]!}.\]
	\end{proof}

@@

% scope of a quantifier bounding it (i.e. it occurs in a sub-formula of
% $\phi$ of the form $\forall x(\psi)$ or $\exists x (\psi)$). 

@@

% $\binom{\binom{n}{2}}{m}$ of those have exactly $m$ edges. \par

@@

% $0\leq p \leq 1$ in the real numbers, is the discrete probability space over

@@

% $n$ tends to infinity. \par

@@

% $\phi$ in $\mathcal{L}$ the probability that $G_n$ satisfies $\phi$ tends

@@

% $\wedge, \vee, \neg, \implies, \dots$, the universal $\forall$ and 

@@

% $\alpha\in (0,1)$ the model $\mathrm{G}(n,n^{-\alpha})$ satisfies a 

@@

% $\mathrm{G}(n,n^{-\alpha})$ does not even obey a convergence law for FO

@@

% $\frac{beta}{2}n$. Many interesting phenomena occur in this regime, being

@@

% $\mathrm{G}_2(n,p)$ is the same model as $\mathrm{G}(n,p)$. \par

@@

% $p$ is of the form $p(n)=\beta n^{-k+1}$. This way the expected total 

@@

% $\mathrm{G}_k(n,p)$ obeys a convergence law for FO logic when
% $p=\beta n^{k-1}$.

@@

%The first order language with signature $\sigma$ deals with strings
%of symbols taken from the alphabet consisting of
% variable symbols $x_1,\dots,x_m,\dots$, the symbols in $\sigma$,
%the logical connectives $\neg, \wedge, \vee$,
%the universal $\forall$ and existential $\exists$ quantifiers,
%the equality symbol, and the parentheses $),($.
%A first order formula is a string obtained after applying the
%following set of rules a finite number of times: 
%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
%	\item If $x_1,x_2$ are variables then $x_1=x_2$ is a formula.
%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
%	and $t_1,\dots, t_{a_i}$ are terms then 
%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
%	\item If $\varphi$ and $\psi$ are formulas, then both
%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
%	a formula.
%	\item If $\varphi$ is a formula and $x$ is a variable then both
%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
%\end{enumerate} 
%
%Let $\varphi$ be a first order formula. An occurrence of a variable 
%in $\varphi$ is called bounded if it is within the scope of
%a quantifier binding it, and is called free otherwise. We
%will assume that the occurrences of any given variable in a first
%order sentence are either all free or all bounded. 
%We will use the notation $\varphi(x_1,\dots, x_n)$ to indicate
%that $x_1, \dots, x_n$ are distinct and they are the free variables
%(i.e. the variables whose occurrences are all free) 
%in $\varphi$. A formula with no free variables is called a sentence,
%and a formula whose variables are all free is called open.
%
%Let $\mathfrak{A}$ be a $\sigma$-structure and $\varphi(x_1,\dots,x_n)$ 
%be a first order sentence. Given a map $\alpha$ from the set
%of free variables $\{x_1,\dots,x_n\}$ to the universe $A$ 
%of $\mathfrak{A}$ we define the relation 
% $\mathfrak{A} \models \varphi[\alpha]$, "$\alpha$ satisfies $\phi$ in $\mathfrak{A}$",
%in the following way:
%\begin{enumerate}[label=(\Roman*),itemsep=0pt, topsep=0pt]
%	\item 
%	\item If $R_i$ is a relation symbol in $\sigma$ with arity $a_i$,
%	and $t_1,\dots, t_{a_i}$ are terms then 
%	$R_i(t_1,\dots,t_{a_i})$ is a formula.
%	\item If $\varphi$ and $\psi$ are formulas, then both
%	$(\varphi \wedge \psi)$ and $(\varphi \vee \psi)$ are formulas.
%	\item If $\varphi$ is a formula then $\neq \varphi$ is also 
%	a formula.
%	\item If $\varphi$ is a formula and $x$ is a variable then both
%	$\forall x \varphi$ and $\exists x\varphi$ are formulas. 
%\end{enumerate} 
%
%

@@

% $[n]:= \{1,\dots, n\}$. We will denote by $S_n$

@@

% $(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
% $[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the

@@

@@

% $H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
% $[n]$. Also, we will write $H(G)$ to denote the 
